My wonderful paper

### 2024-11-06 _manuscript/_tex/index.tex
more writing on the method

@@

@@

Why develop unit tests in software engineering? Because it is difficult
to predict the outcome of a program, especially when the program is
complex.

@@

\begin{itemize}
\item
  multiple tests can be generated to diagnose different aspects of an
  analysis
\item
  good tests

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi})}
  \tightlist
  \item
    are responsive to an unexpected result - accuracy,
  \item
    motivate actions of analysts to investigate the results. This points
    towards a smaller set of independent tests
  \end{enumerate}
\item
  Since both the plan/ outcome expectations can be phrased as unit
  tests, which output binary outcomes, consider using the plan
  expectations as predictors of the outcome expectations. This allows to
  generate the confusion matrix of predicting the outcome with the plan
  expectation.
\item
  For an analysis, ideally, good plan expectations should maximize the
  detection of unexpected outcomes while minimize the false positive
  discovery, which suggest the use of precision and recall (REF) for
  evaluating the performance of the plan expectations.

  \begin{itemize}
  \tightlist
  \item
    precision: the proportion of unexpected results (TP) out of all the
    predicted unexpected results (TP + FP)
  \item
    recall: the proportion of unexpected results (TP) out of all the
    actual unexpected results (TP + FN)
  \end{itemize}
\item
  A logic regression (ref) is used to model the relationship between the
  plan and outcome expectations. (justify the use of Logic regression)
\item
  on independence of the tests
\end{itemize}

@@

\begin{itemize}
\item
  how to systematically simulate data is still unknown, sensitivity of
  the simulation to the results
\item
  plotting is a critical way to check data and they can still be frame
  into a unit test. it is a open problem to how to encode the
  visualization into the unit tests. Maybe a procedure like confirm plot
  (this looks alright to you) and then press the button to continue
\item
  currently no automated way to generate unit tests
\end{itemize}

>>>>

In data analysis, checks are often performed to ensure the quality of
the data and the validity of the model. For data checks,

@@

These checks test on specific aspect of the data or the model but
doesn't reflect the underlying assumption of the data analysts about the
data or the problem context. It may be obvious to see the assumption if
someone is testing for data quality on whether a column in the data
frame is between two values. In a much complex analysis, it is difficult
to trace the assumptions made by the data analysts. Currently, most of
these assumptions are not documented or discussed in the analysis
process, or at least in a machine readable format.

@@

Why develop unit tests in software engineering? Because it is difficult
to predict the outcome of a program, especially when the program is
complex. Because the loss associated with a program failure is costly.

@@

In real-world applications, it is rare to create a set of unit tests can
fully guarantee expected results. On one hand, there is the cost of
effort involved in manually developing all these tests; on the other,
there is the inherent complexity of the problem. (can we - if we're
thriving for detecting 95\% of the cause?). However, the quality of unit
tests can be evaluated by simulated data. One set of tests is considered
better than another if a small set of tests can reliably detect
unexpected outcomes, which brings two criteria in the evaluation metric:
accuracy and parsimony.

Accuracy refers to a set of tests' ability to accurately detect
unexpected outcomes while minimizing false positives and false
negatives. A false positive can indicate (caution or skepticism on
checking the data), whereas a false negative suggests the tests may lack
sensitivity to unexpected outcomes. Since both plan and outcome
expectations can be framed as unit tests with binary outcomes, one
approach is to predict the outcome expectation based on the plan
expectation. Performance of the tests can then be evaluated using
precision and recall metrics from the confusion matrix:

\begin{itemize}
\tightlist
\item
  precision: the proportion of correctly identified unexpected results
  (true positives) out of all the predicted unexpected results (true
  positives + false positives)
\item
  recall: the proportion of correctly identified unexpected results
  (true positives) out of all the actual unexpected results (true
  positives + false negatives)
\end{itemize}

The second criteria is parsimony in the tests. While tests may score
high on accuracy, they may be less effective at explaining the reasons
behind unexpected results. This could happen if a set of tests are all
tangentially related to the cause of the unexpected results, but none
addressing the root cause. It may also occur if the tests are correlated
with one another, leading to redundancy.

\begin{itemize}
\item
  explain mutual information
\item
  explain logic regression
\item
  explain combining precision, recall, and independence together through
  ``means''
\item
  A logic regression (ref) is used to model the relationship between the
  plan and outcome expectations. (justify the use of Logic regression)
\end{itemize}

@@

\begin{itemize}
\item
  how to systematically simulate data is still unknown, sensitivity of
  the simulation to the results
\item
  plotting is a critical way to check data and they can still be frame
  into a unit test. it is a open problem to how to encode the
  visualization into the unit tests. Maybe a procedure like confirm plot
  (this looks alright to you) and then press the button to continue
\item
  currently no automated way to generate unit tests. It is interesting
  to see the automation of generating unit tests, although it requires
  the inputs from experts across a wide array of common scenarios.
\end{itemize}

### 2024-11-06 index.qmd
more writing on the method

- multiple tests can be generated to diagnose different aspects of an analysis 
- good tests 
    1) are responsive to an unexpected result - accuracy, 
    2) motivate actions of analysts to investigate the results. This points towards a smaller set of independent tests

- Since both the plan/ outcome expectations can be phrased as unit tests, which output binary outcomes, consider using the plan expectations as predictors of the outcome expectations. This allows to generate the confusion matrix of predicting the outcome with the plan expectation.

- For an analysis, ideally, good plan expectations should maximize the detection of unexpected outcomes while minimize the false positive discovery, which suggest the use of precision and recall (REF) for evaluating the performance of the plan expectations.

  * precision: the proportion of unexpected results (TP) out of all the predicted unexpected results (TP + FP)
  * recall: the proportion of unexpected results (TP) out of all the actual unexpected results (TP + FN)

@@

* on independence of the tests

@@

* currently no automated way to generate unit tests

>>>>

In real-world applications, it is rare to create a set of unit tests can fully guarantee expected results. On one hand, there is the cost of effort involved in manually developing all these tests; on the other, there is the inherent complexity of the problem. (can we - if we're thriving for detecting 95% of the cause?). However, the quality of unit tests can be evaluated by simulated data. One set of tests is considered better than another if a small set of tests can reliably detect unexpected outcomes, which brings two criteria in the evaluation metric: accuracy and parsimony.

Accuracy refers to a set of tests' ability to accurately detect unexpected outcomes while minimizing false positives and false negatives. A false positive can indicate (caution or skepticism on checking the data), whereas a false negative suggests the tests may lack sensitivity to unexpected outcomes. Since both plan and outcome expectations can be framed as unit tests with binary outcomes, one approach is to predict the outcome expectation based on the plan expectation. Performance of the tests can then be evaluated using precision and recall metrics from the confusion matrix:

  * precision: the proportion of correctly identified unexpected results (true positives) out of all the predicted unexpected results (true positives + false positives)
  * recall: the proportion of correctly identified unexpected results (true positives) out of all the actual unexpected results (true positives + false negatives)

The second criteria is parsimony in the tests. While tests may score high on accuracy, they may be less effective at explaining the reasons behind unexpected results. This could happen if a set of tests are all tangentially related to the cause of the unexpected results, but none addressing the root cause. It may also occur if the tests are correlated with one another, leading to redundancy.

- explain mutual information
- explain logic regression 
- explain combining precision, recall, and independence together through "means"

@@

@@

* currently no automated way to generate unit tests. It is interesting to see the automation of generating unit tests, although it requires the inputs from experts across a wide array of common scenarios.
